Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-04 Paper/paper.tex
General resizing and formatting

% Two Column Format
\documentclass[12pt]{ucthesis}
%this allows us to specify sections to be single or multi column so that things like title page and table of contents are single column
\usepackage{listings}
\usepackage{placeins}
\usepackage{caption}
\usepackage{todonotes}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[letterpaper]{geometry}
\usepackage[overload]{textcase}
\usepackage{verbatim}

@@

Here's a brief example:
\begin{lstlisting}
function Word(startingWord) {
  this.makePlural = function () { ... }

  this.pastTense = function () { ... }

  this.partOfSpeech = function () { ... }
}

function Sentence(listOfWords) {
  this.listOfWords = listOfWords;

  this.isGrammaticallySound = function () { ... }

  this.wordCount = function () {
    return this.listOfWords.length();
  }

  this.makePastTense = function () { ... }

  this.pluralize = function () { ... }
}

@@

This relates to Jasmine is the way that the developer writes Jasmine tests. The idea behind jasmine tests is that they read, as much as possible, like English sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should be able to compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

  it("should be able to subtract numbers", function () {
    var theAnswer = 10;

    expect(12 - 2).toEqual(theAnswer);
  });
});
\end{lstlisting}
The \lstinline{describe} statement creates a test suite to collect related tests under. Each \lstinline{it} statement is generally one test with some number of \lstinline{expect} statements. It may not be particularly pretty, but the above code is quite readable even to someone with no coding experience.

@@

  it("should support async execution of test preparation and expectations", function() {
    runs(function() {
      flag = false;
      value = 0;

@@

// Exports
module.exports = {
  'Exports Suite': {

    'test 1': function () {
      ...
    }

  }
};

// QUnit
suite('QUnit Suite');

test('test 1', function () {
  ...
});
\end{lstlisting}
The developer doesn't gain anything by using one interface over another except the ability to write tests in a way that makes sense to them. There is no standard for writing assertions, as each assertion library is likely to be slightly different.

Mocha's approach to asynchronous testing is quite a bit more straightforward than Jasmine's. In the \lstinline{it(...)} anonymous function, there is passed an additional parameter called \lstinline{done} which is then called when the asynchronous call has finished. This required us to edit the code we were testing to make all the asynchronous calls accept an additional callback, but it was a very small price to pay for extended testability. An example asynchronous test would look like this:
\begin{lstlisting}
describe("Asynch Mocha Test", function () {
  it("look like this", function (done) {
    myAsyncCall(param1, param2, function () {
      // This callback expected to run when async returns

      // Test ...
      // Test ...
      // ...
      done();
    });
  });
});
\end{lstlisting}

@@

QUnit isn't perfect however, QUnit tests are not grouped into suites by default and the syntax for grouping them leaves much to be desired. In order to group tests into ``modules'', as QUnit calls them, the developer writes code like the following:
\begin{lstlisting}
Qunit.module("Module A"); // All code following is grouped into Module A
test("Addition", function () {
  equal(2 + 2, 4, "Two + Two = Four");
  equal(3 + 5, 8, "Three + Five = Eight");
});
test("Subtraction", function () {
  equal(4 - 2, 2, "Four - Two = Two");
  equal(2 - 2, 0, "Two - Two = Zero");
});

@@

QUnit.module("Module B");
// Tests under Module B

// ... Etc
\end{lstlisting}
It is difficult to visually see where one module starts and ends and so grouping and finding the right place to add a test can be a chore.

QUnit's handling of asynchronous tests is similar to Mocha's except instead of adding a parameter to the \lstinline{it} function, the developer calls the \lstinline{asyncTest} function instead. Finally, the developer calls \lstinline{start()} when the asynchronous test is finished. Example:
\begin{lstlisting}
asyncTest("Async Test", function () {
  myAsyncCall(param1, param2, function () {
    // This callback expected to run when async returns

    // Test ...
    // Test ...
    // ...
    start();
  });
});
\end{lstlisting}

@@

// Object
registerSuite({
  name: 'Object Suite',

  'test 1' : function () {
    ...
  }
)
\end{lstlisting}

@@

      // Form submitted, new page loaded.
      assert.ok(browser.success);
      assert.equal(browser.text("title"), "Welcome To Brains Depot");

    })
});
\end{lstlisting}

@@

Here is the new project page:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_new_project.png}
\end{Figure}

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build.png}
\end{Figure}

There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecting the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{npm install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build_filled.png}
\end{Figure}

@@

  // 4) Default task(s).
  grunt.registerTask('default', ['uglify']);

};
\end{lstlisting}

@@

\section{PolyXpress Player Screenshots}
\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_stories.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_chapter_pane.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_chap_instructions.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_chapter_locs.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_marketplace.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_player_loc.png}

@@

\section{PolyXpress Author Screenshots}
\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_author_home.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_event.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_event2.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_chap.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_chap2.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_story.png}

>>>>

% Two Column Format
\documentclass[12pt]{ucthesis}
%this allows us to specify sections to be single or multi column so that things like title page and table of contents are single column
\usepackage{listings}
\usepackage{placeins}
\usepackage{caption}
\usepackage[disable]{todonotes}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[letterpaper]{geometry}
\usepackage[overload]{textcase}
\usepackage{verbatim}

@@

Here's a brief example:
\begin{lstlisting}
function Word(startingWord) {
  this.makePlural = function () { ... }
  this.pastTense = function () { ... }
  this.partOfSpeech = function () { ... }
}

function Sentence(listOfWords) {
  this.listOfWords = listOfWords;
  this.isGrammaticallySound = function () { ... }
  this.wordCount = function () {
    return this.listOfWords.length();
  }
  this.makePastTense = function () { ... }
  this.pluralize = function () { ... }
}

@@

This relates to Jasmine is the way that the developer writes Jasmine tests. The idea behind jasmine tests is that they read, as much as possible, like English sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

  it("should be able to subtract numbers", function () {
    var theAnswer = 10;
    expect(12 - 2).toEqual(theAnswer);
  });
});
\end{lstlisting}
The \lstinline{describe} statement creates a test suite to collect related tests under. Each \lstinline{it} statement is generally one test with some number of \lstinline{expect} statements. It may not be particularly pretty, but the above code is quite readable even to someone with no coding experience.

@@

  it("should support async execution", function() {
    runs(function() {
      flag = false;
      value = 0;

@@

// Exports
module.exports = {
  'Exports Suite': {
    'test 1': function () {
      ...
    }
  }
};

// QUnit
suite('QUnit Suite');
test('test 1', function () {
  ...
});
\end{lstlisting}
The developer doesn't gain anything by using one interface over another except the ability to write tests in a way that makes sense to them. There is no standard for writing assertions, as each assertion library is likely to be slightly different.

Mocha's approach to asynchronous testing is quite a bit more straightforward than Jasmine's. In the \lstinline{it(...)} anonymous function, there is passed an additional parameter called \lstinline{done} which is then called when the asynchronous call has finished. This required us to edit the code we were testing to make all the asynchronous calls accept an additional callback, but it was a very small price to pay for extended testability. An example asynchronous test would look like this:
\begin{lstlisting}
describe("Asynch Mocha Test", function () {
  it("looks like this", function (done) {
    myAsyncCall(param1, param2, function () { 
      // This callback anonymous function expected to run when myAsyncCall returns
      // Test ...
      // Test ...
      // ...
      done();
    });
  });
});
\end{lstlisting}

@@

QUnit isn't perfect however, QUnit tests are not grouped into suites by default and the syntax for grouping them leaves much to be desired. In order to group tests into ``modules'', as QUnit calls them, the developer writes code like the following:
\begin{lstlisting}
Qunit.module("Module A"); // All code following is grouped
test("Addition", function () {
  equal(2 + 2, 4, "Two + Two = Four");
  equal(3 + 5, 8, "Three + Five = Eight");
});
test("Subtraction", function () {
  equal(4 - 2, 2, "Four - Two = Two");
  equal(2 - 2, 0, "Two - Two = Zero");
});

@@

QUnit.module("Module B");
// Tests now grouped under Module B
// ... Etc
\end{lstlisting}
It is difficult to visually see where one module starts and ends and so grouping and finding the right place to add a test can be a chore.

QUnit's handling of asynchronous tests is similar to Mocha's except instead of adding a parameter to the \lstinline{it} function, the developer calls the \lstinline{asyncTest} function instead. Finally, the developer calls \lstinline{start()} when the asynchronous test is finished. Example:
\begin{lstlisting}
asyncTest("Async Test", function () {
  myAsyncCall(param1, param2, function () {
    // This anonymous function expected to run when myAsyncCall returns
    // Test ...
    // Test ...
    // ...
    start();
  });
});
\end{lstlisting}

@@

// Object
registerSuite({
  name: 'Object Suite', 
  'test 1' : function () {
    ...
  },
  'test 2' : ...
)
\end{lstlisting}

@@

      // Form submitted, new page loaded.
      assert.ok(browser.success);
      assert.equal(browser.text("title"), "Welcome To Brains Depot");
    });
});
\end{lstlisting}

@@

Here is the new project page:
\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{magnumCI_new_project.png}
\end{Figure}

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{magnumCI_customize_build.png}
\end{Figure}

There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecting the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{npm install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{magnumCI_customize_build_filled.png}
\end{Figure}

@@

  // 4) Default task(s).
  grunt.registerTask('default', ['uglify']);
};
\end{lstlisting}

@@

\section{PolyXpress Player Screenshots}
\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_stories.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_chapter_pane.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_chap_instructions.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_chapter_locs.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_marketplace.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_player_loc.png}

@@

\section{PolyXpress Author Screenshots}
\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_author_home.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_create_event.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_create_event2.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_create_chap.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_create_chap2.png}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.30\linewidth]{px_create_story.png}
